Working memory performance in adverse environments: Enhanced, impaired, or intact?

### 2024-03-18 manuscript/manuscript.qmd
fix reference error in revised manuscript

In this study, we will estimate associations between latent estimates of WM capacity and updating with three types of adversity: threat, deprivation, and unpredictability. 
Together, these adversity types capture key dimensions in contemporary models of adversity [@ellis_2009; @ellis_2022; @mclaughlin_2016; @mclaughlin_2021]. 
Threat refers to experiences involving the potential for harm imposed by others. 
We focus on perceived neighborhood violence, the extent to which an individual reports having been exposed to acts of violence in their neighborhood. 
Deprivation refers to having a low level of resources. 
We focus on perceived material deprivation, a (perceived) lack of access to material resources. 
Unpredictability refers to variation in material deprivation over time. 
This definition is inspired by, but deviates from the harshness-unpredictability framework, in which unpredictability is defined as stochastic variation in harshness (age-specific rates in morbidity and mortality) over space and time [@ellis_2009; @ellis_2022].
We will not calculate unpredictability in neighborhood threat given that participants have at most six timepoints, and often as few as one or two, which is insufficient to calculate variation over time [@walasek_2023].

>>>>

In this study, we will estimate associations between latent estimates of WM capacity and updating with three types of adversity: threat, deprivation, and unpredictability. 
Together, these adversity types capture key dimensions in contemporary models of adversity [@ellis_2009; @ellis_2022; @mclaughlin_2016; @mclaughlin_2021]. 
Threat refers to experiences involving the potential for harm imposed by others. 
We focus on perceived neighborhood violence, the extent to which an individual reports having been exposed to acts of violence in their neighborhood. 
Deprivation refers to having a low level of resources. 
We focus on perceived material deprivation, a (perceived) lack of access to material resources. 
Unpredictability refers to variation in material deprivation over time. 
This definition is inspired by, but deviates from the harshness-unpredictability framework, in which unpredictability is defined as stochastic variation in harshness (age-specific rates in morbidity and mortality) over space and time [@ellis_2009; @ellis_2022].
We will not calculate unpredictability in neighborhood threat given that participants have at most six timepoints, and often as few as one or two, which is insufficient to calculate variation over time [@walasek_2024].
